---
title: "Simple document"
author: Shihui Zhu
date: 2021-09-16
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
---

I'm an R Markdown document! 

```{r set up, message = FALSE}
library(tidyverse)
```
# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3

Let's write a new code chunk

This code chunk imports the 'tidyverse,' create a dataframe
```{r new_code_chunk, message = FALSE}
# echo, eval, collapse, message
plot_df <-
  tibble(
    x = rnorm(1000, sd = .5),
    y = 1 + 2 * x + rnorm(1000)
  )

ggplot(plot_df, aes(x = x)) + geom_histogram()
ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

# Practices
## My Solution
```{r}
# eval = FALSE
# echo = FALSE
df <- rnorm(500, 1)
log_vec <- df > 0
df_abs <- abs(df)
hist(df_abs)
median(df_abs)
## The median is 1
```
## Learning Assessment Solution
```{r}
# Solution
set.seed(123)
learning_df <- 
  tibble(
    sample = rnorm(500, mean = 1),
    gr_than_0 = sample > 0,
    abs_val = abs(sample)
  )
ggplot(learning_df, aes(x = abs_val)) + geom_histogram(bins = 30)
```
* here is a list
* ### sub-sub section

# Render Package
rmarkdown::render(input = 'name.Rmd', output_format = 'name.html', output_file = 'result/output.html')